Technical Report

### 2024-02-23 Reports/tech_report1.tex
update report

>>>>

\subsection{Compute the gamma of layer 5 for normal 5x100, new pure y-constraints}

This experiment is to  compute the gamma of layer 5 normal 5x100 with new pure-y constraints constraints.

The running code's file name is \verb*|DiamondLipschitz_V0p3_test.py|. And the output file name is \verb*|DL_V0p3_layer5_open_33_node_1.txt|.  It is based on the new pure y-constraints, use MILP model to compute the gamma of layer 5 with open 33 ReLU numbers.

\begin{itemize}
	\item\emph{Experiments Id}: 022200102024

	\item\emph{Open $\ReLU$ number:} Open 33 ReLU nodes for each node.

	\item\emph{Read binary files:} Read \verb*|Diamond_record_6_100_dictionary_with_end_layer3_2024_02_21_13_58_49.b|; this file stores all alpha beta gamma of nodes of all layers for the same network, and the gamma of layer 3 that is computed by new version.
\end{itemize}

\begin{itemize}
	\item \emph{Log:} \verb*|DL_V0p3_layer5_open_33_node_1.txt|.

	\item \emph{Total time:} 26809.2s.

	\item \emph{Key results:} The average gamma of this layer is:  0.7776875638377869

	The average solution for gamma of this layer is:  0.7549862461111381

	\item  \emph{Binary file:} \verb*|Diamond_record_6_100_dictionary_with_end_layer7_2024_02_23_09_28_54.b|. This file stores the gammas in this test.
